\documentclass[10pt, conference, compsocconf]{IEEEtran}

\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
  \DeclareGraphicsExtensions{.pdf,.jpeg,.jpg,.png,.pdf}
\else
  \usepackage[dvips]{graphicx}
  \DeclareGraphicsExtensions{.eps}
\fi

\graphicspath{{./images/}}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{epsfig}
\usepackage{booktabs}

\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

\title{Overlay Architectures enabling Cloud Computing for Multi-Level Security Environments}

%\author{\IEEEauthorblockN{Christopher C. Lamb}
%\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
%University of New Mexico\\
%Albuquerque, NM, USA\\
%cclamb@ece.unm.edu}
%\and
%\IEEEauthorblockN{Gregory L. Heileman}
%\IEEEauthorblockA{Department of Electrical and Computer Engineering\\
%University of New Mexico\\
%Albuquerque, NM, USA\\
%heileman@ece.unm.edu}
%}

\maketitle

\begin{abstract}
Herein,  we consider how overlay architectures can be deployed in order to support usage management in cloud computing.  We contrast filter-centric perimeter and policy-centric overlay approaches toward usage management of sensitive content from the perspective of cross-domain solutions and then demonstrate a path from current systems to distributed policy-centric overlay methods.  We first cover the need for overlay networks supporting usage management by highlighting the pending migration to utility computing models and the current shortcomings of those kinds of systems from a variety of perspectives.  We also briefly cover the state of usage management within these kinds of systems, also examining the known state of the art in proposed cross domain solutions.  We then compare and contrast the advantages of policy-based overlay systems to solving usage management issues over sensitive materials within multi-level security environments. We then demonstrate a migration path from current to future solutions.  We close with our current and future directions of research. 
\end{abstract}

\begin{IEEEkeywords}
usage management; overlay networks; cross domain solutions;

\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\input{content/introduction}
\input{content/current-system-analysis}
\input{content/taxonomy}

\section{Conclusion and Future Work}
In this paper, we covered the current state of cross-domain solutions, the limitations of cloud computing systems, and the characteristics of future solutions to enable cloud-centric information flow control.  We then presented a taxonomy of possible overlay system network architectures addressing these needs embodying a path from current solutions to advanced systems capable of intelligent content control.  We closed the paper by elucidating advantages of these overlay systems over current filter-centric perimeter deployed solutions.

Future work in this area is currently focused on developing prototypical $\beta$, $\gamma$, and $\delta$ systems.  $\phi$ systems are well represented in current operational networks, and we have developed an operational prototype $\alpha$ level system.  After these systems are developed, we will demonstrate the effectiveness of these kinds of architectures, collecting relevant system statistics addressing throughput rates, evaluation performance, and policy flexibility to validate the expectations advocated herein.

\bibliographystyle{IEEEtranBST/IEEEtran}
\bibliography{bib/proposal,bib/drm}

\end{document}


