\documentclass[10pt,letterpaper]{letter}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

\makeatletter
\let\@texttop\relax
\makeatother

\address{Christopher C. Lamb \\
7400 Yarwood St. NE \\
Albuquerque, NM 87109} 
\signature{Christopher C. Lamb} 
\begin{document} 
\begin{letter}{Professor Nasir Ghani \\
Department of Electrical \& Computer Engineering \\
MSC01 1100 \\
1 University of New Mexico \\
ECE Bldg., Room 125 \\
Albuquerque, NM 87131-0001} 
\opening{Professor Ghani:} 
 
I am writing to petition for the substitution of CS 554, 587 and 550 for ECE 536 as my minor core course for my PhD program.  To begin with, I did in fact sit for my qualifying exam covering material from ECE 536, and passed at the PhD level.  Furthermore, the content covered within those CS courses more than covers the content within ECE 536 as it addresses operating systems software topics, compiler construction topics, and the formal specification of computing languages.

I would also like to explicitly request the inclusion of CS 554 within my program of studies.  I took this course in the Spring of 2004.  Though slightly outside the usual time window, the material covered in this course is still relevant as it covered classic compiler construction techniques detailed within Aho et. al.'s classic book \underline{Compilers: Principles, Techniques, and Tools} with application to building a working C language compiler.
 
\closing{Thank you for your consideration,} 
%\cc{Cclist} 
%\ps{adding a postscript} 
%\encl{list of enclosed material} 
\end{letter} 
\end{document}