\section{Characteristics}
\label{section:characteristics}
Examining content at each network node or router point can certainly impact performance and by extension availability.  Furthermore, we need to establish that this kind of dynamic dispatch will actually guarantee delivery along the most secure path.  We can help to increase the throughput of the network overall by taking advantage of the volatility characteristics of the network.  With respect to delivery, we need to show that by selecting optimum paths at given network points the overall selected path will have the appropriate security characteristics outlined by any policy associated with delivered content.

To begin with, we propose that in a given aggregate path between two points if we make local decisions with respect to routing based on specific security criteria at interleaving points the path as a whole will adhere to those security criteria.  Essentially, this implies that we can use a greedy algorithm with respect to security and routing and that the algorithm will yield an optimal security path.  It is important to recognize that this is key to establishing a secure route between two specific points.  Furthermore, in a given route, that route must be viewed temporally as well, in that each link may not be optimal when the delivered data element reaches a destination, but each link was optimal at the time it was selected, and by extension, when the aggregate path is reviewed, it would likewise be optimal with respect to time of traversal.  Finally, local nodes may very well have knowledge about the local environment that cannot be known by a centralized routing authority.  Allowing local routing decisions with respect to security can help take advantage of this locality.



\color{red}
PROOF HERE
\color{black}

We likewise would like to be able to establish certain optimizations with respect to known system state.  Specifically, when we look at a given edge leading away from a node in a path, that edge has certain information associated with it that facilitates routing decisions.  These parameters could be the known state of the network, beliefs with respect to potential route compromise, or a known state of cyber-attack.  These parameters could effect an entire network or just a single edge between two nodes.

\color{red}
I. What are the areas of concern? routing (via greedy alg.) and efficiency (via dynamic programming)

II. How do we know greedy alg. wrt security will work?
A. why is this important?
B. how would it be applied?
C. Outline proof
1. proof


III. How do we know dynamic programming wrt efficency will work? what are the limits?

IV. Wrap up?


What kind of characteristics do we care about? 

more rigor over layers and anlysis here.  Rigorous proof of capabilities wrt content evaluation? prove overlapping subproblems and optimal substructure, and constraints thereof.
\color{black}