\section{Introduction}

\begin{frame}
\frametitle{Our Group and Current Work}
Our group has roots in digital rights management, machine learning and neural networks, and semantic analysis.
\pause
\newline
\newline
We are working on how to manage sensitive content in computer networks.  We are looking at three areas at this point:
\pause
\begin{itemize}
\item \textit{Routing} --- How can we control how sensitive information is routed over the internet? When and why is this appropriate, how can we do it, and where?
\pause
\item \textit{Redaction} --- If we dynamically redact information from transmitted content, what are the implications? how can we go about doing this?
\pause
\item \textit{Usage Management} --- After content has been redacted, how can we control content after delivery? when do we want to do this? why is it appropriate, and how can we implement this?
\end{itemize}
\pause
\begin{center}
\textbf{Simulations $\Rightarrow$ Cloud $\Rightarrow$ SDN (Openflow)}
\end{center}
\end{frame}

\begin{frame}
\frametitle{What We're Doing}
This is a sample of our preliminary work.  The accepted paper is six months old, and we've progressed since then.
\pause
\newline
\newline
Today I'm going to cover the submitted paper and touch on current progress as well.  This will involve:
\pause
\begin{itemize}
\item \textit{Covering Motivation and Current Work}
\pause
\item \textit{Describing Shortcomings of Current State}
\pause
\item \textit{Discussing Characteristics of Future Solutions}
\pause
\item \textit{Reviewing our Solution Taxonomy}
\pause
\item \textit{Discussing Simulations and Current Directions}
\end{itemize}
\begin{center}
\pause
\textbf{Please, any comments with respect to alternative avenues, collaboration, or resource pooling is more than welcome! That's why I'm here.}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Introduction}
Distributed enterprise computing systems are facing a troubling future.  They are:
\pause
\begin{itemize}
\item \textit{Expensive} --- They do not use current commercial resources and use costly partitioning schemes
\pause
\item \textit{Unreliable} --- Too reliant on outmoded security approaches
\pause
\item \textit{Slow} --- Sensitive information is manually reviewed too often leading to the right people being unable to get the right information in time 
\end{itemize}
\
\newline
\pause
They need to be re-imagined to take advantage of radical shifts in computational provisioning.
\newline
\newline
\pause
\textit{Federal computer systems are a prime example of these kind of problematic distributed systems, and demonstrate the difficulty in implementing new technical solutions.}
\end{frame}